---
title: "First Try Replication"
author: "Nikolina Filiposki but code from previous authors (partly)"
date: "2024-04-07"
output:
  html_document:
    toc: true
    toc_float: true
    css: css/lab.css
  pdf_document:
    toc: yes
header-includes:
   - \usepackage[default]{sourcesanspro}
   - \usepackage[T1]{fontenc}
mainfont: SourceSansPro
---

```{r, setup, include = FALSE }
knitr::opts_chunk$set(echo = TRUE)

p_needed <-
  c("viridis", 
    "knitr", 
    "MASS", 
    "pROC", 
    "tidyverse",
    "stargazer",
    "haven",
    "estimatr",
    "dplyr",
    "fixest",
    "ggplot2",
    "tidyr",
    "lme4")
    #"modelsummery") # not running yet, idk why 


packages <- rownames(installed.packages())
p_to_install <- p_needed[!(p_needed %in% packages)]

if (length(p_to_install) > 0) {
  install.packages(p_to_install)
}
sapply(p_needed, require, character.only = TRUE)

# This is an option for stargazer tables
#stargazer_opt <- ifelse(knitr::is_html_output(), "html")
# "latex"
```



```{r, load multilevel}
load("raw-data/multilevel_1-5-22.Rdata")
```



```{r, data wrangeling part }
# Load the Data
load("cses_imd_r/cses_imd.RData")

# Just in case backup
cses <- cses_imd

# Special case: DEU_2002 (telephone and mail-back combined here)
cses <- cses %>%
  mutate(IMD1004 = ifelse(IMD1004 %in% c("DEU12002", "DEU22002"), "DEU_2002", IMD1004))

# Special case: GRC_2015 (two time points Jan 2015 and Sep 2015 combined here)
cses <- cses %>%
  mutate(IMD1004 = ifelse(IMD1004 %in% c("GRC12015", "GRC22015"), "GRC_2015", IMD1004))



# Select variables of interest
selected_vars <- select(cses, 
                        starts_with("IMD1006_"),
                        starts_with("IMD1005"), 
                        starts_with("IMD1004"),
                        starts_with("IMD3008_"),
                        starts_with("IMD1008_"),
                        starts_with("IMD5000_"),
                        starts_with("IMD5001_"), 
                        starts_with("IMD5003_"), 
                        starts_with("IMD5005_"))

# Choose country and year of interest (case selection like Adams et al. 2022)

# Generate a vector of countries
countries <- c("AUS", "AUT", "CAN", "DNK", "FIN", "FRA", "DEU", "GBR", "GRC", "ISL",
               "IRL", "ISR", "NLD", "NZL", "NOR", "PRT", "ESP", "SWE", "CHE", "USA")

# Generate a vector of years
years <- 1996:2017

# Create an empty vector to store combinations
cy_interest <- c()

# Loop through each combination of country and year
for (country in countries) {
  for (year in years) {
    # Check if the combination exists in  dataset
    if (any(grepl(paste0(country, "_", year), selected_vars$IMD1004))) {
      # If it exists, add it to the vector
      cy_interest <- c(cy_interest, paste(country, year, sep = "_"))
    }
  }
}

# Check 
print(cy_interest)

# Use filter() to select rows where IMD1004 is one of the countries in years of interest
selected_dataset <- filter(selected_vars, IMD1004 %in% cy_interest)

# View the selected dataset
# print(selected_dataset)

# Name identifier variable 'ID'

#names(selected_dataset)[names(selected_dataset) == "IMD1005"] <- "ID"
#names(multilevel_data)[names(multilevel_data) == "ID"] <- "ID"


# Merge datasets on common identifier
#merged_dataset <- left_join(multilevel_data, selected_dataset, by = "ID", all = TRUE)  # Change all = TRUE if you want to keep all rows


 
 rm(cses_imd)
 rm(cses)
 rm(selected_vars)
# rm(selected_d)
# rm(multilevel_data)

```

```{r, filter like variable }
# Filter out rows with values 96, 97, and 98 from variables IMD3008_A to IMD3008_I
selected_d <- selected_dataset %>%
  filter_at(vars(starts_with("IMD3008_")), all_vars(!. %in% c(96, 97, 98)))
```



```{r, modify vote share}
# Divide variables by 100
selected_d[, c("IMD5001_A", "IMD5001_B", "IMD5001_C", "IMD5001_D", 
         "IMD5001_E", "IMD5001_F", "IMD5001_G", "IMD5001_H", "IMD5001_I")] <- 
  selected_d[, c("IMD5001_A", "IMD5001_B", "IMD5001_C", "IMD5001_D", 
           "IMD5001_E", "IMD5001_F", "IMD5001_G", "IMD5001_H", "IMD5001_I")] / 100


# Divide variables by 100
selected_d[, c("IMD5005_A", "IMD5005_B", "IMD5005_C", "IMD5005_D", 
         "IMD5005_E", "IMD5005_F", "IMD5005_G", "IMD5005_H", "IMD5005_I")] <- 
  selected_d[, c("IMD5005_A", "IMD5005_B", "IMD5005_C", "IMD5005_D", 
           "IMD5005_E", "IMD5005_F", "IMD5005_G", "IMD5005_H", "IMD5005_I")] / 100

rm(selected_dataset)

# check if we have missings in IMD1001_a to _I (vote share)
check_values <- function(data, cols, target_value) {
  for (col in cols) {
    if (any(data[[col]] == target_value, na.rm = TRUE)) {
      print(paste(col, "has a value of", target_value))
    }
  }
}

# Columns to check
cols_to_check <- c("IMD5001_A", "IMD5001_B", "IMD5001_C", "IMD5001_D", "IMD5001_E", "IMD5001_F", "IMD5001_G", "IMD5001_H", "IMD5001_I")

# Check the values of these columns for the target value 0.999
check <- check_values(selected_d, cols_to_check, 9.97)
print(check)



```

Try out different API approches here...

First Reijan(2020)
```{r, Reijan 2020}
calculate_AP <- function(data) {
  # List of party preference variables (IMD3008_A to IMD3008_I)
  party_pref_vars <- c("IMD3008_A", "IMD3008_B", "IMD3008_C", "IMD3008_D", 
                       "IMD3008_E", "IMD3008_F", "IMD3008_G", "IMD3008_H", "IMD3008_I")
  
  # List of vote share variables (IMD5001_A to IMD5001_I)
  vote_share_vars <- c("IMD5001_A", "IMD5001_B", "IMD5001_C", "IMD5001_D", 
                       "IMD5001_E", "IMD5001_F", "IMD5001_G", "IMD5001_H", "IMD5001_I")
  
  # Initialize a vector to store AP scores for each party
  AP_scores <- matrix(0, nrow = nrow(data), ncol = length(party_pref_vars),
                      dimnames = list(NULL, party_pref_vars))
  
  # Loop through each respondent
  for (i in 1:nrow(data)) {
    # Get party preference and vote share data for the current respondent
    party_pref <- unlist(data[i, party_pref_vars])
    vote_share <- unlist(data[i, vote_share_vars])
    
    # Exclude missing values (99)
    valid_ratings <- which(!is.na(party_pref) & party_pref != 99)
    
    # Calculate the AP score for each party
    for (j in 1:length(party_pref_vars)) {
      if (j %in% valid_ratings) {
        in_party_pref <- party_pref[j]
        in_party_vote_share <- vote_share[j]
        combined_out_party_vote_share <- sum(vote_share[-j])
        out_party_prefs <- party_pref[-j]
        
        # Calculate the weighted difference between in-party and out-party preferences
        weighted_diff <- (in_party_pref - out_party_prefs) * (in_party_vote_share - combined_out_party_vote_share)
        
        # Sum up the weighted differences
        AP_scores[i, j] <- sum(weighted_diff)
      }
    }
  }
  
  # Return the relative AP scores for each party
  return(AP_scores)
}

# Selected_d is the dataset containing party preferences and vote shares
AP_scores <- calculate_AP(selected_d)
print(AP_scores)

#rm(AP_scores)
```


Second Wagner (2021)
$$
\begin{equation}
\text{Spread}_i = \sqrt{\frac{1}{n_p} \sum_{p=1}^{P} (\text{like}_{ip} - \bar{\text{like}}_i)^2}
\end{equation}


$$

```{r, Wagner 2021 Spread_i}
calculate_affective_polarization <- function(data) {
  # List of party preference variables (likeip)
  party_pref_vars <- c("IMD3008_A", "IMD3008_B", "IMD3008_C", "IMD3008_D", 
                       "IMD3008_E", "IMD3008_F", "IMD3008_G", "IMD3008_H", "IMD3008_I")
  
  # Initialize a vector to store affective polarization scores for each respondent
  affective_polarization_scores <- numeric(nrow(data))
  
  # Loop through each respondent
  for (i in 1:nrow(data)) {
    # Get party preference data for the current respondent
    party_pref <- unlist(data[i, party_pref_vars])
    
    # Exclude missing values (99)
    valid_ratings <- which(!is.na(party_pref) & party_pref != 99)
    
    # Calculate the weighted average party affect for the current respondent
    likei <- mean(party_pref[valid_ratings])
    
    # Calculate the spread for the current respondent
    spread_i <- sqrt(sum((party_pref[valid_ratings] - likei)^2) / length(valid_ratings))
    
    # Store the affective polarization score for the current respondent
    affective_polarization_scores[i] <- spread_i
  }
  
  # Return the affective polarization scores for each respondent
  return(affective_polarization_scores)
}

# Example usage:
# Assuming 'data' is your dataset containing party preferences
# Replace 'data' with the actual name of your dataset
affective_polarization_scores <- calculate_affective_polarization(selected_d)
print(affective_polarization_scores)

```


$$
\begin{equation}
Spread_i = \sqrt{\sum_{p=1}^{P} v_p \times (like_{ip} - like_i)^2}
\end{equation}
$$


where:
- \(Spread_i\) is the Weighted Affective Polarization score for respondent \(i\),
- \(P\) is the total number of parties,
- \(v_p\) is the vote share of party \(p\) (measured as a proportion with a range from 0 to 1),
- \(like_{ip}\) is the preference score given by respondent \(i\) for party \(p\), and
- \(like_i\) is the weighted average party affect for respondent \(i\).

$$
like_i = \sum_{p=1}^{P} (v_p \times like_{ip})
$$




```{r, spread like Wagner}
calculate_weighted_AP <- function(data) {
  # List of party preference variables (IMD3008_A to IMD3008_I)
  party_pref_vars <- c("IMD3008_A", "IMD3008_B", "IMD3008_C", "IMD3008_D", 
                       "IMD3008_E", "IMD3008_F", "IMD3008_G", "IMD3008_H", "IMD3008_I")
  
  # List of vote share variables (IMD5001_A to IMD5001_I)
  vote_share_vars <- c("IMD5001_A", "IMD5001_B", "IMD5001_C", "IMD5001_D", 
                       "IMD5001_E", "IMD5001_F", "IMD5001_G", "IMD5001_H", "IMD5001_I")
  
  # Initialize a vector to store weighted AP scores for each respondent
  weighted_AP_scores <- numeric(nrow(data))
  
  # Loop through each respondent
  for (i in 1:nrow(data)) {
    # Get party preference and vote share data for the current respondent
    party_pref <- unlist(data[i, party_pref_vars])
    vote_share <- unlist(data[i, vote_share_vars])
    
    # Exclude missing values (99)
    valid_ratings <- which(!is.na(party_pref) & party_pref != 99)
    
    # Calculate the weighted average party affect for the current respondent
    likei <- sum(party_pref[valid_ratings] * vote_share[valid_ratings])
    
    # Calculate the spread for the current respondent
    spread_i <- sqrt(sum((party_pref[valid_ratings] - likei)^2 * vote_share[valid_ratings]))
    
    # Store the weighted AP score for the current respondent
    weighted_AP_scores[i] <- spread_i
  }
  
  # Return the weighted AP scores for each respondent
  return(weighted_AP_scores)
}


weighted_AP_scores <- calculate_weighted_AP(selected_d)
print(weighted_AP_scores)

```



$$
\begin{equation}
Distance_i = \sqrt{\frac{1}{n_p} \sum_{p=1}^{P} v_p \times (like_{ip} - like_{\text{max},i})^2}
\end{equation}

$$


```{r, distance i}
calculate_mean_distance <- function(data) {
  # List of party preference variables (IMD3008_A to IMD3008_I)
  party_pref_vars <- c("IMD3008_A", "IMD3008_B", "IMD3008_C", "IMD3008_D", 
                       "IMD3008_E", "IMD3008_F", "IMD3008_G", "IMD3008_H", "IMD3008_I")
  
  # List of vote share variables (IMD5001_A to IMD5001_I)
  vote_share_vars <- c("IMD5001_A", "IMD5001_B", "IMD5001_C", "IMD5001_D", 
                       "IMD5001_E", "IMD5001_F", "IMD5001_G", "IMD5001_H", "IMD5001_I")
  
  # Initialize a vector to store mean-distance scores for each respondent
  mean_distance_scores <- numeric(nrow(data))
  
  # Loop through each respondent
  for (i in 1:nrow(data)) {
    # Get party preference and vote share data for the current respondent
    party_pref <- unlist(data[i, party_pref_vars])
    vote_share <- unlist(data[i, vote_share_vars])
    
    # Exclude missing values (99)
    valid_ratings <- which(!is.na(party_pref) & party_pref != 99)
    
    # Find the most-liked party
    most_liked_party_index <- which.max(party_pref[valid_ratings])
    likemax <- party_pref[valid_ratings][most_liked_party_index]
    
    # Calculate the mean-distance score for the current respondent
    num_parties <- length(valid_ratings)
    likemax_square <- likemax^2
    sum_distance <- sum((party_pref[valid_ratings] - likemax)^2 * vote_share[valid_ratings])
    mean_distance <- sqrt(sum_distance / num_parties)
    
    # Store the mean-distance score for the current respondent
    mean_distance_scores[i] <- mean_distance
  }
  
  # Return the mean-distance scores for each respondent
  return(mean_distance_scores)
}

mean_distance_scores <- calculate_mean_distance(selected_d)
print(mean_distance_scores)



```




Need that score for dyadic data (own approach from Wagner formula): 

$$
\text{Spread}_{ip} = \sqrt{v_p \times (\text{like}_{ip} - \bar{\text{like}}_i)^2}

$$
+ $Spread_ip$ represents the affective polarization score for respondent $i$ towards party $p$.
+ $v_p$ is the vote share of party $p$ (measured as a percentage with a range from 0 to 100).
+ $like_ip$ is the like-dislike score assigned by respondent $i$ for party $p$.
+ $likeˉ_i$ is the average like-dislike score assigned by respondent $i$ across all parties.

$$
like_i = \sum_{p=1}^{P} (v_p \times like_{ip})
$$
```{r AP with selected_d (not accounting for France + special cases)}
calculate_affective_polarization_party <- function(data, respondent_ids) {
  party_pref_vars <- c("IMD3008_A", "IMD3008_B", "IMD3008_C", "IMD3008_D", 
                       "IMD3008_E", "IMD3008_F", "IMD3008_G", "IMD3008_H", "IMD3008_I")
  
  vote_share_vars <- c("IMD5001_A", "IMD5001_B", "IMD5001_C", "IMD5001_D", 
                       "IMD5001_E", "IMD5001_F", "IMD5001_G", "IMD5001_H", "IMD5001_I")
  
  affective_polarization_scores <- matrix(0, nrow = nrow(data), ncol = length(party_pref_vars) + 1)  # +1 for the respondent ID
  
  for (i in 1:nrow(data)) {
    party_pref <- unlist(data[i, party_pref_vars])
    vote_share <- unlist(data[i, vote_share_vars]) 
    
    # Initialize affective polarization scores for the current respondent
    affective_polarization_row <- rep(0, length(party_pref))
    
    # Calculate the average like-dislike score for the current respondent
    valid_ratings <- which(!is.na(party_pref) & party_pref != 99)
    likei <- sum(party_pref[valid_ratings] * vote_share[valid_ratings])
    
    # Calculate the affective polarization score for non-missing party preferences
    valid_parties <- party_pref != 99
    affective_polarization_row[valid_parties] <- sqrt(vote_share[valid_parties] * (party_pref[valid_parties] - likei)^2)
    
    # Add respondent ID to the beginning of the row
    affective_polarization_row <- c(respondent_ids[i], affective_polarization_row)
    
    # Store the affective polarization scores for the current respondent
    affective_polarization_scores[i, ] <- affective_polarization_row
  }
  
  
  return(affective_polarization_scores)
}



affective_polarization_party_scores <- calculate_affective_polarization_party(selected_d, selected_d$IMD1005)
print(affective_polarization_party_scores)



# Convert matrix to data frame
AP_party_df <- as.data.frame(affective_polarization_party_scores)

# Add row names as a column
#AP_party_df$Respondent <- rownames(AP_party_df)


AP_party_df <- AP_party_df %>% 
  rename(
    ID = V1, 
    A = V2,
    B = V3,
    C = V4,
    D = V5,
    E = V6,
    F = V7,
    G = V8,
    H = V9,
    I = V10
  )


# Reshape data frame into long format
AP_party_long <- pivot_longer(AP_party_df, cols = -ID, names_to = "party_to", values_to = "WAP")
```



```{r, experiment correct but without ID}
calculate_affective_polarization_party <- function(data) {
  party_pref_vars <- c("IMD3008_A", "IMD3008_B", "IMD3008_C", "IMD3008_D", 
                       "IMD3008_E", "IMD3008_F", "IMD3008_G", "IMD3008_H", "IMD3008_I")
  
  vote_share_vars <- c("IMD5001_A", "IMD5001_B", "IMD5001_C", "IMD5001_D", 
                       "IMD5001_E", "IMD5001_F", "IMD5001_G", "IMD5001_H", "IMD5001_I")
  
  affective_polarization_scores <- matrix(0, nrow = nrow(data), ncol = length(party_pref_vars))
  
  for (i in 1:nrow(data)) {
    party_pref <- unlist(data[i, party_pref_vars])
    vote_share <- unlist(data[i, vote_share_vars]) 
    
    # Initialize affective polarization scores for the current respondent
    affective_polarization_row <- rep(0, length(party_pref))
    
    # Calculate the average like-dislike score for the current respondent
    valid_ratings <- which(!is.na(party_pref) & party_pref != 99)
    likei <- sum(party_pref[valid_ratings] * vote_share[valid_ratings])
    
    # Calculate the affective polarization score for non-missing party preferences
    valid_parties <- party_pref != 99
    affective_polarization_row[valid_parties] <- sqrt(vote_share[valid_parties] * (party_pref[valid_parties] - likei)^2)
    
    # Store the affective polarization scores for the current respondent
    affective_polarization_scores[i, ] <- affective_polarization_row
  }
  
  return(affective_polarization_scores)
}

# Example usage:
affective_polarization_party_scores <- calculate_affective_polarization_party(selected_d)
print(affective_polarization_party_scores)



# Convert matrix to data frame
AP_party_df <- as.data.frame(affective_polarization_party_scores)

# Add row names as a column
AP_party_df$Respondent <- rownames(AP_party_df)


AP_party_df <- AP_party_df %>% 
  rename(
    A = V1,
    B = V2,
    C = V3,
    D = V4,
    E = V5,
    F = V6,
    G = V7,
    H = V8,
    I = V9
  )


# Reshape data frame into long format
AP_party_long <- pivot_longer(AP_party_df, cols = -Respondent, names_to = "party_to", values_to = "WAP")

```

Make several data sets: 

# 1 For all country-year where vote share and preference fits 

```{r create data set for where vote share and preference fits}
cases_full <- c("AUS_1996",
                 "AUS_2004",
                 "AUS_2007",
                 "AUS_2013",
                 "AUT_2008", 
                 "AUT_2013",
                 "AUT_2017",
                 "CAN_1997",
                 "CAN_2004",
                 "CAN_2008",
                 "CAN_2011",
                 "CAN_2015",
                 "DNK_1998",
                 "DNK_2001",
                 "DNK_2007",
                 "FIN_2003",
                 "FIN_2007",
                 "FIN_2011",
                 "FRA_2007",
                 "DEU_1998",
                 "DEU_2009", 
                 "DEU_2013",
                 "DEU_2017", 
                 "GBR_1997", 
                 "GBR_2005",
                 "GBR_2015",
                 "GRC_2009", 
                 "GRC_2012",
                 "GRC_2015", 
                 "ISL_1999", 
                 "ISL_2003",
                 "ISL_2007",
                 "ISL_2009",
                 "ISL_2013",
                 "IRL_2002",
                 "IRL_2007",
                 "IRL_2011",
                 "IRL_2016",
                 "ISR_1996",
                 "ISR_2003",
                 "ISR_2006",
                 "ISR_2013",
                 "NLD_2002",
                 "NLD_2006",
                 "NLD_2010",
                 "NZL_1996",
                 "NZL_2002",
                 "NZL_2008",
                 "NZL_2011",
                 "NZL_2014",
                 "NOR_1997",
                 "NOR_2001",
                 "NOR_2005",
                 "NOR_2009",
                 "NOR_2013",
                 "PRT_2002",
                 "PRT_2005",
                 "PRT_2009",
                 "ESP_1996",
                 "ESP_2000",
                 "ESP_2004",
                 "SWE_1998",
                 "SWE_2002",
                 "SWE_2014",
                 "CHE_1999",
                 "CHE_2003",
                 "CHE_2007",
                 "CHE_2011",
                 "USA_1996",
                 "USA_2008",
                 "USA_2012",
                 "USA_2016"
           )

Full_selected_d <- filter(selected_d, IMD1004 %in% cases_full)
```

# 2 For France 

```{r create data set for two cases from France}
cases_fra <- c("FRA_2002", "FRA_2012")

FRA_selected_d <- filter(selected_d, IMD1004 %in% cases_fra)
```

# 3 For all country_year where vote share and preference does not fit
```{r create data set where vote share and preference do not fit}
#cases_fail <- c("DEU_2002", "DEU_2005", "NLD_1998", "PRT_2015", "SWE_2006", "USA_2004")
# Fail_selected_d <- filter(selected_d, IMD1004 %in% cases_fail)

DEU_2002 <- c("DEU_2002")
DEU_2005 <- c("DEU_2005")
NLD_1998 <- c("NLD_1998")
PRT_2015 <- c("PRT_2015")
SWE_2006 <- c("SWE_2006")
USA_2004 <- c("USA_2004")
ESP_2008 <- c("ESP_2008")

# Set preference columns to missing where vote share is missing

# DEU_2002
DEU_2002_d <- filter(selected_d, IMD1004 %in% DEU_2002)
# G and H
DEU_2002_d <- DEU_2002_d %>%
  mutate(IMD3008_G = 99, IMD3008_H = 99)

# DEU_2005
DEU_2005_d <- filter(selected_d, IMD1004 %in% DEU_2005)
# G 
DEU_2002_d <- DEU_2002_d %>%
  mutate(IMD3008_G = 99)

# NLD_1998 
NLD_1998_d <- filter(selected_d, IMD1004 %in% NLD_1998)
# G
NLD_1998_d <- NLD_1998_d %>%
  mutate(IMD3008_G = 99)

# PRT_2015
PRT_2015_d <- filter(selected_d, IMD1004 %in% PRT_2015)
# H
PRT_2015_d <- PRT_2015_d %>%
  mutate(IMD3008_H = 99)

# SWE_2006
SWE_2006_d <- filter(selected_d, IMD1004 %in% SWE_2006)
# I
SWE_2006_d <- SWE_2006_d %>%
  mutate(IMD3008_I = 99)

# USA_2004
USA_2004_d <- filter(selected_d, IMD1004 %in% USA_2004)
# C
USA_2004_d <- USA_2004_d %>%
  mutate(IMD3008_C = 99)

# ESP_2008
ESP_2008_d <- filter(selected_d, IMD1004 %in% ESP_2008)
# G and H
ESP_2008_d <- ESP_2008_d %>%
  mutate(IMD3008_G = 99, IMD3008_H = 99)

# Combine data sets 
combined_df <- bind_rows(DEU_2002_d, DEU_2005_d, NLD_1998_d, PRT_2015_d, 
                         SWE_2006_d, USA_2004_d, ESP_2008_d)

rm(DEU_2002_d)
rm(DEU_2005_d)
rm(NLD_1998_d)
rm(PRT_2015_d)
rm(SWE_2006_d)
rm(USA_2004_d)
rm(ESP_2008_d)

```


```{r, AP with ID correct one}
calculate_affective_polarization_party <- function(data, respondent_ids) {
  party_pref_vars <- c("IMD3008_A", "IMD3008_B", "IMD3008_C", "IMD3008_D", 
                       "IMD3008_E", "IMD3008_F", "IMD3008_G", "IMD3008_H", "IMD3008_I")
  
  vote_share_vars <- c("IMD5001_A", "IMD5001_B", "IMD5001_C", "IMD5001_D", 
                       "IMD5001_E", "IMD5001_F", "IMD5001_G", "IMD5001_H", "IMD5001_I")
  
  affective_polarization_scores <- matrix(0, nrow = nrow(data), ncol = length(party_pref_vars) + 1)  # +1 for the respondent ID
  
  for (i in 1:nrow(data)) {
    party_pref <- unlist(data[i, party_pref_vars])
    vote_share <- unlist(data[i, vote_share_vars]) 
    
    # Initialize affective polarization scores for the current respondent
    affective_polarization_row <- rep(0, length(party_pref))
    
    # Calculate the average like-dislike score for the current respondent
    valid_ratings <- which(!is.na(party_pref) & party_pref != 99)
    likei <- sum(party_pref[valid_ratings] * vote_share[valid_ratings])
    
    # Calculate the affective polarization score for non-missing party preferences
    valid_parties <- party_pref != 99
    affective_polarization_row[valid_parties] <- sqrt(vote_share[valid_parties] * (party_pref[valid_parties] - likei)^2)
    
    # Add respondent ID to the beginning of the row
    affective_polarization_row <- c(respondent_ids[i], affective_polarization_row)
    
    # Store the affective polarization scores for the current respondent
    affective_polarization_scores[i, ] <- affective_polarization_row
  }
  
  
  return(affective_polarization_scores)
}

AP_Full_scores <- calculate_affective_polarization_party(Full_selected_d, Full_selected_d$IMD1005)
print(AP_Full_scores)


# Convert matrix to data frame
AP_party_df <- as.data.frame(affective_polarization_party_scores)

# Add row names as a column
#AP_party_df$Respondent <- rownames(AP_party_df)


AP_party_df <- AP_party_df %>% 
  rename(
    ID = V1, 
    A = V2,
    B = V3,
    C = V4,
    D = V5,
    E = V6,
    F = V7,
    G = V8,
    H = V9,
    I = V10
  )


# Reshape data frame into long format
AP_party_long <- pivot_longer(AP_party_df, cols = -ID, names_to = "party_to", values_to = "WAP")

```


```{r, AP for two cases of France}
calculate_AP_FRA <- function(data, respondent_ids) {
  party_pref_vars <- c("IMD3008_A", "IMD3008_B", "IMD3008_C", "IMD3008_D", 
                       "IMD3008_E", "IMD3008_F", "IMD3008_G", "IMD3008_H", "IMD3008_I")
  
  vote_share_vars <- c("IMD5005_A", "IMD5005_B", "IMD5005_C", "IMD5005_D", 
                       "IMD5005_E", "IMD5005_F", "IMD5005_G", "IMD5005_H", "IMD5005_I")
  
  affective_polarization_scores <- matrix(0, nrow = nrow(data), ncol = length(party_pref_vars) + 1)  # +1 for the respondent ID
  
  for (i in 1:nrow(data)) {
    party_pref <- unlist(data[i, party_pref_vars])
    vote_share <- unlist(data[i, vote_share_vars]) 
    
    # Initialize affective polarization scores for the current respondent
    affective_polarization_row <- rep(0, length(party_pref))
    
    # Calculate the average like-dislike score for the current respondent
    valid_ratings <- which(!is.na(party_pref) & party_pref != 99)
    likei <- sum(party_pref[valid_ratings] * vote_share[valid_ratings])
    
    # Calculate the affective polarization score for non-missing party preferences
    valid_parties <- party_pref != 99
    affective_polarization_row[valid_parties] <- sqrt(vote_share[valid_parties] * (party_pref[valid_parties] - likei)^2)
    
    # Add respondent ID to the beginning of the row
    affective_polarization_row <- c(respondent_ids[i], affective_polarization_row)
    
    # Store the affective polarization scores for the current respondent
    affective_polarization_scores[i, ] <- affective_polarization_row
  }
  
#  colnames(affective_polarization_scores) <- c("ID", paste0("Affective_Polarization_", LETTERS[1:length(party_pref_vars)]))
  #colnames(affective_polarization_scores)[1] <- "ID"  # Rename the first column only
  
  return(affective_polarization_scores)
}

AP_FRA_scores <- calculate_AP_FRA(FRA_selected_d, FRA_selected_d$IMD1005)
print(AP_FRA_scores)

# partei of null setzten 
```


```{r, AP special six }
calculate_affective_polarization_party <- function(data, respondent_ids) {
  party_pref_vars <- c("IMD3008_A", "IMD3008_B", "IMD3008_C", "IMD3008_D", 
                       "IMD3008_E", "IMD3008_F", "IMD3008_G", "IMD3008_H", "IMD3008_I")
  
  vote_share_vars <- c("IMD5001_A", "IMD5001_B", "IMD5001_C", "IMD5001_D", 
                       "IMD5001_E", "IMD5001_F", "IMD5001_G", "IMD5001_H", "IMD5001_I")
  
  affective_polarization_scores <- matrix(0, nrow = nrow(data), ncol = length(party_pref_vars) + 1)  # +1 for the respondent ID
  
  for (i in 1:nrow(data)) {
    party_pref <- unlist(data[i, party_pref_vars])
    vote_share <- unlist(data[i, vote_share_vars]) 
    
    # Initialize affective polarization scores for the current respondent
    affective_polarization_row <- rep(0, length(party_pref))
    
    # Calculate the average like-dislike score for the current respondent
    valid_ratings <- which(!is.na(party_pref) & party_pref != 99)
    likei <- sum(party_pref[valid_ratings] * vote_share[valid_ratings])
    
    # Calculate the affective polarization score for non-missing party preferences
    valid_parties <- party_pref != 99
    affective_polarization_row[valid_parties] <- sqrt(vote_share[valid_parties] * (party_pref[valid_parties] - likei)^2)
    
    # Add respondent ID to the beginning of the row
    affective_polarization_row <- c(respondent_ids[i], affective_polarization_row)
    
    # Store the affective polarization scores for the current respondent
    affective_polarization_scores[i, ] <- affective_polarization_row
  }
  
  
  return(affective_polarization_scores)
}

AP_six_spe <- calculate_affective_polarization_party(combined_df, combined_df$IMD1005)
print(AP_six_spe)
```







```{r, combine matricies}

AP_all_scores <- rbind(AP_Full_scores, AP_FRA_scores, AP_six_spe)# AP_Fail_scores #  AP_FRA_scores

# Convert matrix to data frame
AP_party_df <- as.data.frame(AP_all_scores)

# Add row names as a column
#AP_party_df$Respondent <- rownames(AP_party_df)


AP_party_df <- AP_party_df %>% 
  rename(
    ID = V1, 
    A = V2,
    B = V3,
    C = V4,
    D = V5,
    E = V6,
    F = V7,
    G = V8,
    H = V9,
    I = V10
  )


# Reshape data frame into long format
AP_party_long <- pivot_longer(AP_party_df, cols = -ID, names_to = "party_to", values_to = "WAP")
```




```{r, merge AP_party_long mit multilevel_data }

# Perform the merge
merged_data <- merge(AP_party_long, multilevel_data, by = c("party_to", "ID"))

```


```{r, data wrangeling merged_data}
## Removing smaller parties

merged_data <- merged_data %>%
  filter(to_prior_seats >= 4) %>%
  select(rile_distance_s, prior_coalition, prior_opposition, econ_distance_s, society_distance_s,
         year, country, party_dislike, party_like, cntryyr, to_pfeml, to_prior_seats, to_mp_number, WAP) %>%
  na.omit()

# check
sum(is.na(merged_data$to_pfeml))

hist(merged_data[merged_data$cntryyr == "Great Britain2015", "to_pfeml"])

```


```{r, perform first multilevel analysis}

# Adams et al. 2023 
table1.1 <-lm(party_like ~ to_pfeml + as.factor(cntryyr), data = merged_data)
summary(table1.1)


table1 <- lm(WAP ~ to_pfeml + as.factor(cntryyr), data = merged_data)
summary(table1)

merged_data$to_pfeml <- as.numeric(merged_data$to_pfeml)
merged_data$WAP <- as.numeric(merged_data$WAP)

mlm_1 <- lmer(WAP ~ to_pfeml +
                (1 + to_pfeml | country),
              data = merged_data)

summary(mlm_1)

ranef(mlm_1)




table2 <- lm(WAP ~ to_pfeml + as.factor(country), data = merged_data)
summary(table2)

#table3 <- lm(WAP ~ to_pfeml + as.factor(year), data = merged_data)
#summary(table3)

count1 <- sum(merged_data$cntryyr == "Australia1996")
print(count1)

count2 <- sum(multilevel_data$cntryyr == "Australia1996")
print(count2)

summary(merged_data$cntryyr)

#load("raw-data/dyadic_data_1-4-22.Rdata")


print_values_for_condition <- function(data, condition_col, condition_val, target_col) {
  # Filter the data based on the condition
  filtered_data <- data[data[[condition_col]] == condition_val, ]
  
  # Print the values of the target column for the filtered rows
  if (nrow(filtered_data) > 0) {
    print(filtered_data[[target_col]])
  } else {
    print(paste("No rows found where", condition_col, "is equal to", condition_val))
  }
}


# Print the values of IMD5001_A for rows where IMD1004 is "France2002"
print_values_for_condition(selected_d, "IMD1004", "FRA_2002", "IMD5005_I")

print_values_for_condition(selected_d, "IMD1004", "FRA_2012", "IMD5001_A")

print_values_for_condition(merged_data, "cntryyr", "Spain2008", "to_pfeml")

```


```{r, simulation (working)}
nsim <- 10000

# Step 1: Get the regression coefficients
#   NOTE: We are only using fixed effects
beta_hat <- fixef(mlm_1)

# Step 2: Generate sampling distribution

# Step 2.1: Get the variance-covariance matrix.
V_hat <-  vcov(mlm_1)

# Step 2.2: Draw from the multivariate normal distribution.
S <- mvrnorm(nsim, beta_hat, V_hat)

# Additional Step 2.3: Add random effects

# varying intercept
S[, "(Intercept)"] <- 
  S[, "(Intercept)"] + 
  ranef(mlm_1)$country["Spain", "(Intercept)"]
# varying slope
S[, "to_pfeml"] <- 
  S[, "to_pfeml"] + 
  ranef(mlm_1)$country["Spain", "to_pfeml"]



# Step 3: Choose interesting covariate values. 
# Make sure the matrix multiplication also works for single scenarios
min_to_pfeml <- min(merged_data$to_pfeml[merged_data$country == "Spain"], na.rm = T)
max_to_pfeml <- max(merged_data$to_pfeml[merged_data$country == "Spain"], na.rm = T)
to_pfeml_seq <- seq(min_to_pfeml, max_to_pfeml,
                     length.out = 100)

scenario <- cbind(1, to_pfeml_seq)

# Step 4: Calculate Quantities of Interest - 
# Expected Values
EV <- S %*% t(scenario)

# Step 5: Summarize
ev_mean <- apply(EV, 2, mean)
ev_ci <- apply(EV, 2, quantile, c(0.025, 0.975))
```

```{r, plot simulation}
plot(x = to_pfeml_seq,
     y = ev_mean,
     ylim = c(0.1, 1),
     xlim = c(0.0, 0.5),
     type = "l",
     lwd = 1.5,
     main = "Female share and WAP in Spain",
     font.main = 1,
     ylab = "Expected value of WAP",
     xlab = "Average female share",
     las = 1)
lines(x = to_pfeml_seq,
      y = ev_ci["2.5%",],
      lty = "dashed",
      lwd = 1.5)
lines(x = to_pfeml_seq,
      y = ev_ci["97.5%",],
      lty = "dashed",
      lwd = 1.5)
```



```{r simulation with years 20 countries}
# Step 1: Modify the Model
mlm_1 <- lmer(WAP ~ to_pfeml  + (1 + to_pfeml | country), data = merged_data)
summary(mlm_1)

# Step 2: Update the Simulation Process
nsim <- 10000

# Step 2.1: Get the regression coefficients and variance-covariance matrix
beta_hat <- fixef(mlm_1)
V_hat <- vcov(mlm_1)

# Step 2.2: Draw from the multivariate normal distribution
S <- mvrnorm(nsim, beta_hat, V_hat)

# Step 2.3: Add random effects for all countries
country_names <- unique(merged_data$country)
num_countries <- length(country_names)

# Step 3: Create Covariate Scenarios for Years
min_to_pfeml <- min(merged_data$to_pfeml, na.rm = TRUE)
max_to_pfeml <- max(merged_data$to_pfeml, na.rm = TRUE)
to_pfeml_seq <- seq(min_to_pfeml, max_to_pfeml, length.out = 100)

years <- seq(2000, 2020, by = 1)

# Step 4: Calculate Expected Values for Each Country
EV_list <- list()
ev_mean_list <- list()
ev_ci_list <- list()

for (i in 1:num_countries) {
  country <- country_names[i]
  
  EV_country <- matrix(NA, nrow = length(to_pfeml_seq), ncol = length(years))
  for (j in 1:length(years)) {
    year <- years[j]
    
    # Filter data for the specific country and year
    country_data <- merged_data[merged_data$country == country & merged_data$year == year, ]
    
    # Create scenario for the country and year
    scenario <- cbind(1, to_pfeml_seq, rep(year, length(to_pfeml_seq)))
    
    # Calculate expected values
    EV <- S %*% t(scenario)
    
    # Store the results
    EV_country[, j] <- apply(EV, 2, mean)
  }
  
  EV_list[[country]] <- EV_country
}

# Set up the plot layout with adjusted margins
par(mfrow = c(5, 4), mar = c(4, 4, 2, 1))  

for (i in 1:num_countries) {
  country <- country_names[i]
  EV_country <- EV_list[[country]]
  
  plot(NULL, xlim = range(to_pfeml_seq), ylim = range(unlist(EV_list)), type = "n",
       main = paste("Female share and WAP in", country),
       xlab = "Average female share",
       ylab = "Expected value of WAP")
  
  for (j in 1:length(years)) {
    lines(x = to_pfeml_seq, y = EV_country[, j], col = j, lwd = 1.5)
  }
}

# Reset plot layout to default
par(mfrow = c(1, 1))


```


```{r, only country without confidence interval }

# Step 1: Modify the Model
mlm_1 <- lmer(WAP ~ to_pfeml + (1 + to_pfeml | country), data = merged_data)
summary(mlm_1)

# Step 2: Update the Simulation Process
nsim <- 10000

# Step 2.1: Get the regression coefficients and variance-covariance matrix
beta_hat <- fixef(mlm_1)
V_hat <- vcov(mlm_1)

# Step 2.2: Draw from the multivariate normal distribution
S <- mvrnorm(nsim, beta_hat, V_hat)

# Step 2.3: Add random effects for all countries
country_names <- unique(merged_data$country)
num_countries <- length(country_names)

# Step 3: Create Covariate Scenarios for Countries
min_to_pfeml <- min(merged_data$to_pfeml, na.rm = TRUE)
max_to_pfeml <- max(merged_data$to_pfeml, na.rm = TRUE)
to_pfeml_seq <- seq(min_to_pfeml, max_to_pfeml, length.out = 100)

# Step 4: Calculate Expected Values for Each Country
EV_list <- list()
ev_mean_list <- list()
ev_ci_list <- list()

for (i in 1:num_countries) {
  country <- country_names[i]
  
  EV_country <- matrix(NA, nrow = length(to_pfeml_seq), ncol = 1)
  scenario <- cbind(1, to_pfeml_seq)
  
  for (j in 1:nsim) {
    # Add random effects for the country
    S_sample <- S[j, ]
    S_sample[1] <- S_sample[1] + ranef(mlm_1)$country[country, "(Intercept)"]
    S_sample[2] <- S_sample[2] + ranef(mlm_1)$country[country, "to_pfeml"]
    
    # Calculate expected values
    EV <- S_sample %*% t(scenario)
    
    # Store the results
    EV_country[, 1] <- EV_country[, 1] + EV[, 1]
  }
  
  EV_list[[country]] <- EV_country / nsim
}

# Step 5: Plot the Results for Each Country
par(mfrow = c(5, 4), mar = c(4, 4, 2, 1))  # Set up the plot layout

for (i in 1:num_countries) {
  country <- country_names[i]
  EV_country <- EV_list[[country]]
  
  plot(to_pfeml_seq, EV_country[, 1], type = "l",
       main = paste("Female share and WAP in", country),
       xlab = "Average female share",
       ylab = "Expected value of WAP")
}

# Reset plot layout to default
par(mfrow = c(1, 1))

```


```{r, simulation of country with CI}

# Step 1: Modify the Model
mlm_1 <- lmer(WAP ~ to_pfeml + (1 + to_pfeml | country), data = merged_data)
summary(mlm_1)

# Step 2: Update the Simulation Process
nsim <- 1000  # Adjust the number of simulations as needed

# Step 2.1: Get the regression coefficients and variance-covariance matrix
beta_hat <- fixef(mlm_1)
V_hat <- vcov(mlm_1)

# Step 2.2: Draw from the multivariate normal distribution
S <- mvrnorm(nsim, beta_hat, V_hat)

# Step 2.3: Add random effects for all countries
country_names <- unique(merged_data$country)
num_countries <- length(country_names)

# Step 3: Create Covariate Scenarios for Countries
scenario_list <- list()

for (i in 1:num_countries) {
  country <- country_names[i]
  
  # Filter data for the specific country
  country_data <- merged_data[merged_data$country == country, ]
  
  # Calculate min and max to_pfeml for the country
  min_to_pfeml_country <- min(country_data$to_pfeml, na.rm = TRUE)
  max_to_pfeml_country <- max(country_data$to_pfeml, na.rm = TRUE)
  
  # Create scenario for the country
  to_pfeml_seq_country <- seq(min_to_pfeml_country, max_to_pfeml_country, length.out = 100)
  scenario_country <- cbind(1, to_pfeml_seq_country)
  
  # Store the scenario
  scenario_list[[country]] <- scenario_country
}

# Step 4: Calculate Expected Values and Confidence Intervals for Each Country
EV_list <- list()
ci_list <- list()

for (i in 1:num_countries) {
  country <- country_names[i]
  scenario_country <- scenario_list[[country]]
  
  EV_country <- matrix(NA, nrow = length(scenario_country), ncol = nsim)
  
  for (j in 1:nsim) {
    # Add random effects for the country
    S_sample <- S[j, ]
    S_sample[1] <- S_sample[1] + ranef(mlm_1)$country[country, "(Intercept)"]
    S_sample[2] <- S_sample[2] + ranef(mlm_1)$country[country, "to_pfeml"]
    
    # Calculate expected values
    EV <- S_sample %*% t(scenario_country)
    
    
    # Store the results
    EV_country[, j] <- EV[, 1]
  }
  
  # Calculate confidence intervals
  ci <- apply(EV_country, 1, quantile, c(0.025, 0.975))
  
  # Store the results
  EV_list[[country]] <- rowMeans(EV_country)
  ci_list[[country]] <- ci
}

# Step 5: Plot the Results for Each Country
par(mfrow = c(5, 4), mar = c(4, 4, 2, 1))  # Adjust margin size

for (i in 1:num_countries) {
  country <- country_names[i]
  
  # Get country-specific scenario, EV, and CI
  scenario_country <- scenario_list[[country]]
  EV_country <- EV_list[[country]]
  ci_country <- ci_list[[country]]
  
  # Plot expected values and confidence intervals
  plot(scenario_country[, 2], EV_country, type = "l", col = "black",
       main = paste("Female share and WAP in", country),
       xlab = "Average female share",
       ylab = "Expected value of WAP")
  
  lines(scenario_country[, 2], ci_country[1, ], col = "black", lty = "dashed")
  lines(scenario_country[, 2], ci_country[2, ], col = "black", lty = "dashed")
}

# Reset plot layout to default
par(mfrow = c(1, 1))




```


```{r, simulation correct one yet}

# List of countries
countries <- c("Australia", "Austria", "Canada", "Switzerland", "Germany", "Denmark", 
               "Finland", "France", "Great Britain", "Greece", "Ireland", "Iceland", 
               "Israel", "Netherlands", "New Zealand", "Norway", "Portugal", "Spain", 
               "Sweden", "United States of America") 

# Number of simulations
nsim <- 10000

# Step 1: Get the regression coefficients
# NOTE: We are only using fixed effects
beta_hat <- fixef(mlm_1)

# Step 2: Generate sampling distribution
# Step 2.1: Get the variance-covariance matrix
V_hat <- vcov(mlm_1)

# Step 2.2: Draw from the multivariate normal distribution
S <- mvrnorm(nsim, beta_hat, V_hat)

# Function to plot for a given country
plot_country <- function(country) {
  # Add random effects for the country
  S_country <- S
  S_country[, "(Intercept)"] <- S_country[, "(Intercept)"] + ranef(mlm_1)$country[country, "(Intercept)"]
  S_country[, "to_pfeml"] <- S_country[, "to_pfeml"] + ranef(mlm_1)$country[country, "to_pfeml"]
  
  # Get the range of 'to_pfeml' for the country
  min_to_pfeml <- min(merged_data$to_pfeml[merged_data$country == country], na.rm = TRUE)
  max_to_pfeml <- max(merged_data$to_pfeml[merged_data$country == country], na.rm = TRUE)
  to_pfeml_seq <- seq(min_to_pfeml, max_to_pfeml, length.out = 100)
  
  
  # Create the scenario matrix
  scenario <- cbind(1, to_pfeml_seq)
  
  # Calculate Quantities of Interest - Expected Values
  EV <- S_country %*% t(scenario)
  
  # Summarize
  ev_mean <- apply(EV, 2, mean)
  ev_ci <- apply(EV, 2, quantile, c(0.025, 0.975))
  
  # Plot
  plot(x = to_pfeml_seq,
       y = ev_mean,
       ylim = c(0.1, 5),
       xlim = c(0.0, 0.8),
       type = "l",
       lwd = 1.5,
       main = paste("Female share and WAP in", country),
       font.main = 1,
       ylab = "Expected value of WAP",
       xlab = "Average female share",
       las = 1)
  lines(x = to_pfeml_seq,
        y = ev_ci["2.5%", ],
        lty = "dashed",
        lwd = 1.5)
  lines(x = to_pfeml_seq,
        y = ev_ci["97.5%", ],
        lty = "dashed",
        lwd = 1.5)
}

# Loop through each country and plot
par(mfrow = c(5, 4), mar = c(5, 5, 2, 1))# Adjust layout to fit all plots in one view
for (country in countries) {
  plot_country(country)
}

```





```{r, plot data usisng heatmap (not a good idea tbh)}


# Convert matrix to data frame
#weighted_AP_df <- as.data.frame(weighted_AP_dyadic)

# Add row names as a column
#weighted_AP_df$Respondent <- rownames(weighted_AP_df)

# Convert WAP to numeric
AP_party_long$WAP <- as.numeric(AP_party_long$WAP)

# Reshape data frame into long format
weighted_AP_long <- pivot_longer(weighted_AP_df, cols = -Respondent, names_to = "Party", values_to = "WAP")

# Generate heatmap
ggplot(data = AP_party_long, aes(x = party_to, y = Respondent, fill = WAP)) +
  geom_tile(color = "white") +
  scale_fill_gradient(low = "lightblue", high = "darkblue") +
  labs(title = "Dyadic Weighted AP Scores", x = "Party", y = "Respondent") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1))


```


```{r, try to plot the data unsing KDE}
ggplot(data = AP_party_long, aes(x = WAP)) +
  geom_density(fill = "skyblue", color = "blue", alpha = 0.5) +
  labs(title = "Kernel Density Estimation (KDE) Plot of Dyadic Weighted AP Scores", x = "WAP Score", y = "Density") +
  xlim(0, 3)+
  theme_minimal()
```






