---
title: "First Try Replication"
author: "Nikolina Filiposki but code from previous authors (partly)"
date: "2024-04-07"
output:
  html_document:
    toc: true
    toc_float: true
    css: css/lab.css
  pdf_document:
    toc: yes
header-includes:
   - \usepackage[default]{sourcesanspro}
   - \usepackage[T1]{fontenc}
mainfont: SourceSansPro
---

```{r, setup, include = FALSE }
knitr::opts_chunk$set(echo = TRUE)

p_needed <-
  c("viridis", 
    "knitr", 
    "MASS", 
    "pROC", 
    "tidyverse",
    "stargazer",
    "haven",
    "estimatr",
    "dplyr",
    "fixest",
    "ggplot2",
    "tidyr")
    #"modelsummery") # not running yet, idk why 


packages <- rownames(installed.packages())
p_to_install <- p_needed[!(p_needed %in% packages)]

if (length(p_to_install) > 0) {
  install.packages(p_to_install)
}
sapply(p_needed, require, character.only = TRUE)

# This is an option for stargazer tables
#stargazer_opt <- ifelse(knitr::is_html_output(), "html")
# "latex"
```



```{r, load multilevel}
load("raw-data/multilevel_1-5-22.Rdata")
```



```{r, AP }
# Load the Data
load("cses_imd_r/cses_imd.RData")

# Just in case backup
cses <- cses_imd

# Select variables of interest
selected_vars <- select(cses, 
                        starts_with("IMD1006_"),
                        starts_with("IMD1005"), 
                        starts_with("IMD1004"),
                        starts_with("IMD3008_"),
                        starts_with("IMD1008_"),
                        starts_with("IMD5000_"),
                        starts_with("IMD5001_"), 
                        starts_with("IMD5003_"), 
                        starts_with("IMD5005_"))

# Choose country and year of interest (case selection like Adams et al. 2022)

# Generate a vector of countries
countries <- c("AUS", "AUT", "CAN", "DNK", "FIN", "FRA", "DEU", "GBR", "GRC", "ISL",
               "IRL", "ISR", "NLD", "NZL", "NOR", "PRT", "ESP", "SWE", "CHE", "USA")

# Generate a vector of years
years <- 1996:2017

# Create an empty vector to store combinations
cy_interest <- c()

# Loop through each combination of country and year
for (country in countries) {
  for (year in years) {
    # Check if the combination exists in  dataset
    if (any(grepl(paste0(country, "_", year), selected_vars$IMD1004))) {
      # If it exists, add it to the vector
      cy_interest <- c(cy_interest, paste(country, year, sep = "_"))
    }
  }
}

# Check 
print(cy_interest)

# Use filter() to select rows where IMD1004 is one of the countries in years of interest
selected_dataset <- filter(selected_vars, IMD1004 %in% cy_interest)

# View the selected dataset
# print(selected_dataset)

# Name identifier variable 'ID'

#names(selected_dataset)[names(selected_dataset) == "IMD1005"] <- "ID"
#names(multilevel_data)[names(multilevel_data) == "ID"] <- "ID"


# Merge datasets on common identifier
#merged_dataset <- left_join(multilevel_data, selected_dataset, by = "ID", all = TRUE)  # Change all = TRUE if you want to keep all rows


 
 rm(cses_imd)
 rm(cses)
 rm(selected_vars)
# rm(selected_d)
# rm(multilevel_data)

```

```{r}
# Filter out rows with values 96, 97, and 98 from variables IMD3008_A to IMD3008_I
selected_d <- selected_dataset %>%
  filter_at(vars(starts_with("IMD3008_")), all_vars(!. %in% c(96, 97, 98)))

# Filter out rows with value 99 in variables IMD3008_A to IMD3008_F
# selected_d <- selected_d %>%
#   filter_at(vars(ends_with("_A"), ends_with("_B"), ends_with("_C"), ends_with("_D"), ends_with("_E"), # ends_with("_F")), 
#             all_vars(!. %in% c(99)))
```



```{r, modify vote share}
# Divide variables by 100
selected_d[, c("IMD5001_A", "IMD5001_B", "IMD5001_C", "IMD5001_D", 
         "IMD5001_E", "IMD5001_F", "IMD5001_G", "IMD5001_H", "IMD5001_I")] <- 
  selected_d[, c("IMD5001_A", "IMD5001_B", "IMD5001_C", "IMD5001_D", 
           "IMD5001_E", "IMD5001_F", "IMD5001_G", "IMD5001_H", "IMD5001_I")] / 100

rm(selected_dataset)

```

Try out different API approches here...

First Reijan(2020)
```{r, Reijan 2020}
calculate_AP <- function(data) {
  # List of party preference variables (IMD3008_A to IMD3008_I)
  party_pref_vars <- c("IMD3008_A", "IMD3008_B", "IMD3008_C", "IMD3008_D", 
                       "IMD3008_E", "IMD3008_F", "IMD3008_G", "IMD3008_H", "IMD3008_I")
  
  # List of vote share variables (IMD5001_A to IMD5001_I)
  vote_share_vars <- c("IMD5001_A", "IMD5001_B", "IMD5001_C", "IMD5001_D", 
                       "IMD5001_E", "IMD5001_F", "IMD5001_G", "IMD5001_H", "IMD5001_I")
  
  # Initialize a vector to store AP scores for each party
  AP_scores <- matrix(0, nrow = nrow(data), ncol = length(party_pref_vars),
                      dimnames = list(NULL, party_pref_vars))
  
  # Loop through each respondent
  for (i in 1:nrow(data)) {
    # Get party preference and vote share data for the current respondent
    party_pref <- unlist(data[i, party_pref_vars])
    vote_share <- unlist(data[i, vote_share_vars])
    
    # Exclude missing values (99)
    valid_ratings <- which(!is.na(party_pref) & party_pref != 99)
    
    # Calculate the AP score for each party
    for (j in 1:length(party_pref_vars)) {
      if (j %in% valid_ratings) {
        in_party_pref <- party_pref[j]
        in_party_vote_share <- vote_share[j]
        combined_out_party_vote_share <- sum(vote_share[-j])
        out_party_prefs <- party_pref[-j]
        
        # Calculate the weighted difference between in-party and out-party preferences
        weighted_diff <- (in_party_pref - out_party_prefs) * (in_party_vote_share - combined_out_party_vote_share)
        
        # Sum up the weighted differences
        AP_scores[i, j] <- sum(weighted_diff)
      }
    }
  }
  
  # Return the relative AP scores for each party
  return(AP_scores)
}

# Selected_d is the dataset containing party preferences and vote shares
AP_scores <- calculate_AP(selected_d)
print(AP_scores)

#rm(AP_scores)
```


Second Wagner (2021)
$$
\begin{equation}
\text{Spread}_i = \sqrt{\frac{1}{n_p} \sum_{p=1}^{P} (\text{like}_{ip} - \bar{\text{like}}_i)^2}
\end{equation}


$$

```{r, Wagner 2021 Spread_i}
calculate_affective_polarization <- function(data) {
  # List of party preference variables (likeip)
  party_pref_vars <- c("IMD3008_A", "IMD3008_B", "IMD3008_C", "IMD3008_D", 
                       "IMD3008_E", "IMD3008_F", "IMD3008_G", "IMD3008_H", "IMD3008_I")
  
  # Initialize a vector to store affective polarization scores for each respondent
  affective_polarization_scores <- numeric(nrow(data))
  
  # Loop through each respondent
  for (i in 1:nrow(data)) {
    # Get party preference data for the current respondent
    party_pref <- unlist(data[i, party_pref_vars])
    
    # Exclude missing values (99)
    valid_ratings <- which(!is.na(party_pref) & party_pref != 99)
    
    # Calculate the weighted average party affect for the current respondent
    likei <- mean(party_pref[valid_ratings])
    
    # Calculate the spread for the current respondent
    spread_i <- sqrt(sum((party_pref[valid_ratings] - likei)^2) / length(valid_ratings))
    
    # Store the affective polarization score for the current respondent
    affective_polarization_scores[i] <- spread_i
  }
  
  # Return the affective polarization scores for each respondent
  return(affective_polarization_scores)
}

# Example usage:
# Assuming 'data' is your dataset containing party preferences
# Replace 'data' with the actual name of your dataset
affective_polarization_scores <- calculate_affective_polarization(selected_d)
print(affective_polarization_scores)

```


$$
\begin{equation}
Spread_i = \sqrt{\sum_{p=1}^{P} v_p \times (like_{ip} - like_i)^2}
\end{equation}
$$


where:
- \(Spread_i\) is the Weighted Affective Polarization score for respondent \(i\),
- \(P\) is the total number of parties,
- \(v_p\) is the vote share of party \(p\) (measured as a proportion with a range from 0 to 1),
- \(like_{ip}\) is the preference score given by respondent \(i\) for party \(p\), and
- \(like_i\) is the weighted average party affect for respondent \(i\).

$$
like_i = \sum_{p=1}^{P} (v_p \times like_{ip})
$$



```{r}
calculate_weighted_AP <- function(data) {
  # List of party preference variables (IMD3008_A to IMD3008_I)
  party_pref_vars <- c("IMD3008_A", "IMD3008_B", "IMD3008_C", "IMD3008_D", 
                       "IMD3008_E", "IMD3008_F", "IMD3008_G", "IMD3008_H", "IMD3008_I")
  
  # List of vote share variables (IMD5001_A to IMD5001_I)
  vote_share_vars <- c("IMD5001_A", "IMD5001_B", "IMD5001_C", "IMD5001_D", 
                       "IMD5001_E", "IMD5001_F", "IMD5001_G", "IMD5001_H", "IMD5001_I")
  
  # Initialize a vector to store weighted AP scores for each respondent
  weighted_AP_scores <- numeric(nrow(data))
  
  # Loop through each respondent
  for (i in 1:nrow(data)) {
    # Get party preference and vote share data for the current respondent
    party_pref <- unlist(data[i, party_pref_vars])
    vote_share <- unlist(data[i, vote_share_vars])
    
    # Exclude missing values (99)
    valid_ratings <- which(!is.na(party_pref) & party_pref != 99)
    
    # Calculate the weighted average party affect for the current respondent
    likei <- sum(party_pref[valid_ratings] * vote_share[valid_ratings])
    
    # Calculate the spread for the current respondent
    spread_i <- sqrt(sum((party_pref[valid_ratings] - likei)^2 * vote_share[valid_ratings]))
    
    # Store the weighted AP score for the current respondent
    weighted_AP_scores[i] <- spread_i
  }
  
  # Return the weighted AP scores for each respondent
  return(weighted_AP_scores)
}


weighted_AP_scores <- calculate_weighted_AP(selected_d)
print(weighted_AP_scores)

```



$$
\begin{equation}
Distance_i = \sqrt{\frac{1}{n_p} \sum_{p=1}^{P} v_p \times (like_{ip} - like_{\text{max},i})^2}
\end{equation}

$$


```{r, distance i}
calculate_mean_distance <- function(data) {
  # List of party preference variables (IMD3008_A to IMD3008_I)
  party_pref_vars <- c("IMD3008_A", "IMD3008_B", "IMD3008_C", "IMD3008_D", 
                       "IMD3008_E", "IMD3008_F", "IMD3008_G", "IMD3008_H", "IMD3008_I")
  
  # List of vote share variables (IMD5001_A to IMD5001_I)
  vote_share_vars <- c("IMD5001_A", "IMD5001_B", "IMD5001_C", "IMD5001_D", 
                       "IMD5001_E", "IMD5001_F", "IMD5001_G", "IMD5001_H", "IMD5001_I")
  
  # Initialize a vector to store mean-distance scores for each respondent
  mean_distance_scores <- numeric(nrow(data))
  
  # Loop through each respondent
  for (i in 1:nrow(data)) {
    # Get party preference and vote share data for the current respondent
    party_pref <- unlist(data[i, party_pref_vars])
    vote_share <- unlist(data[i, vote_share_vars])
    
    # Exclude missing values (99)
    valid_ratings <- which(!is.na(party_pref) & party_pref != 99)
    
    # Find the most-liked party
    most_liked_party_index <- which.max(party_pref[valid_ratings])
    likemax <- party_pref[valid_ratings][most_liked_party_index]
    
    # Calculate the mean-distance score for the current respondent
    num_parties <- length(valid_ratings)
    likemax_square <- likemax^2
    sum_distance <- sum((party_pref[valid_ratings] - likemax)^2 * vote_share[valid_ratings])
    mean_distance <- sqrt(sum_distance / num_parties)
    
    # Store the mean-distance score for the current respondent
    mean_distance_scores[i] <- mean_distance
  }
  
  # Return the mean-distance scores for each respondent
  return(mean_distance_scores)
}

mean_distance_scores <- calculate_mean_distance(selected_d)
print(mean_distance_scores)



```




Need that score for dyadic data (experiment): 

$$
\text{Spread}_{ip} = \sqrt{v_p \times (\text{like}_{ip} - \bar{\text{like}}_i)^2}

$$
+ $Spread_ip$ represents the affective polarization score for respondent $i$ towards party $p$.
+ $v_p$ is the vote share of party $p$ (measured as a percentage with a range from 0 to 100).
+ $like_ip$ is the like-dislike score assigned by respondent $i$ for party $p$.
+ $likeˉ_i$ is the average like-dislike score assigned by respondent $i$ across all parties.





```{r, experiment not correct}
calculate_affective_polarization_party <- function(data) {
  party_pref_vars <- c("IMD3008_A", "IMD3008_B", "IMD3008_C", "IMD3008_D", 
                       "IMD3008_E", "IMD3008_F", "IMD3008_G", "IMD3008_H", "IMD3008_I")
  
  vote_share_vars <- c("IMD5001_A", "IMD5001_B", "IMD5001_C", "IMD5001_D", 
                       "IMD5001_E", "IMD5001_F", "IMD5001_G", "IMD5001_H", "IMD5001_I")
  
  affective_polarization_scores <- matrix(0, nrow = nrow(data), ncol = length(party_pref_vars))
  
  for (i in 1:nrow(data)) {
    party_pref <- unlist(data[i, party_pref_vars])
    vote_share <- unlist(data[i, vote_share_vars]) 
    
    # Initialize affective polarization scores for the current respondent
    affective_polarization_row <- rep(0, length(party_pref))
    
    # Calculate the average like-dislike score for the current respondent
    valid_ratings <- which(!is.na(party_pref) & party_pref != 99)
    likei <- sum(party_pref[valid_ratings] * vote_share[valid_ratings])
    
    # Calculate the affective polarization score for non-missing party preferences
    valid_parties <- party_pref != 99
    affective_polarization_row[valid_parties] <- sqrt(vote_share[valid_parties] * (party_pref[valid_parties] - likei)^2)
    
    # Store the affective polarization scores for the current respondent
    affective_polarization_scores[i, ] <- affective_polarization_row
  }
  
  return(affective_polarization_scores)
}

# Example usage:
affective_polarization_party_scores <- calculate_affective_polarization_party(selected_d)
print(affective_polarization_party_scores)

```




```{r, WAP (non-dyadic)}
calculate_weighted_AP <- function(data) {
  # List of party preference variables (IMD3008_A to IMD3008_I)
  party_pref_vars <- c("IMD3008_A", "IMD3008_B", "IMD3008_C", "IMD3008_D", 
                       "IMD3008_E", "IMD3008_F", "IMD3008_G", "IMD3008_H", "IMD3008_I")
  
  # List of vote share variables (IMD5001_A to IMD5001_I)
  vote_share_vars <- c("IMD5001_A", "IMD5001_B", "IMD5001_C", "IMD5001_D", 
                       "IMD5001_E", "IMD5001_F", "IMD5001_G", "IMD5001_H", "IMD5001_I")
  
  # Initialize a vector to store weighted AP scores for each respondent
  weighted_AP_scores <- numeric(nrow(data))
  
  # Loop through each respondent
  for (i in 1:nrow(data)) {
    # Get party preference and vote share data for the current respondent
    party_pref <- unlist(data[i, party_pref_vars])
    vote_share <- unlist(data[i, vote_share_vars])
    
    # Initialize variables for calculating weighted average party affect and spread
    likei <- 0
    spread_i <- 0
    
    # Loop through each party preference
    for (j in 1:length(party_pref)) {
      # Skip value 99
      if (party_pref[j] == 99) next
      
      # Calculate the weighted average party affect for the current respondent
      likei <- likei + party_pref[j] * vote_share[j]
    }
    
    # Calculate the spread for the current respondent
    for (j in 1:length(party_pref)) {
      # Skip value 99
      if (party_pref[j] == 99) next
      
      spread_i <- spread_i + (party_pref[j] - likei)^2 * vote_share[j]
    }
    spread_i <- sqrt(spread_i)
    
    # Store the weighted AP score for the current respondent
    weighted_AP_scores[i] <- spread_i
  }
  
  # Return the weighted AP scores for each respondent
  return(weighted_AP_scores)
}

weighted_AP_scores <- calculate_weighted_AP(selected_d)
print(weighted_AP_scores)



```

$$
\text{WAP}_{ip} = \sqrt{v_p \times (\text{like}_{ip} - \bar{\text{like}}_i)^2}

$$



```{r, WAP dyadic (currently working with)}
calculate_weighted_AP_dyadic <- function(data) {
  # List of party preference variables (IMD3008_A to IMD3008_I)
  party_pref_vars <- c("IMD3008_A", "IMD3008_B", "IMD3008_C", "IMD3008_D", 
                       "IMD3008_E", "IMD3008_F", "IMD3008_G", "IMD3008_H", "IMD3008_I")
  
  # List of vote share variables (IMD5001_A to IMD5001_I)
  vote_share_vars <- c("IMD5001_A", "IMD5001_B", "IMD5001_C", "IMD5001_D", 
                       "IMD5001_E", "IMD5001_F", "IMD5001_G", "IMD5001_H", "IMD5001_I")
  
  # Initialize a matrix to store weighted AP scores for each respondent-party pair
  num_respondents <- nrow(data)
  num_parties <- length(party_pref_vars)
  weighted_AP_dyadic <- matrix(0, nrow = num_respondents, ncol = num_parties)
  
  # Loop through each respondent
  for (i in 1:num_respondents) {
    # Get party preference and vote share data for the current respondent
    party_pref <- unlist(data[i, party_pref_vars])
    vote_share <- unlist(data[i, vote_share_vars])
    
    # Loop through each party preference
    for (j in 1:num_parties) {
      # Skip value 99
      if (party_pref[j] == 99) next
      
      # Calculate the weighted average party affect for the current respondent
      likei <- sum(party_pref * vote_share)
      
      # Calculate the spread for the current respondent-party pair
      spread_ij <- sqrt((party_pref[j] - likei)^2 * vote_share[j])
      
      # Store the weighted AP score for the current respondent-party pair
      weighted_AP_dyadic[i, j] <- spread_ij
    }
  }
  
  # Return the matrix of weighted AP scores for each respondent-party pair
  return(weighted_AP_dyadic)
}

weighted_AP_dyadic <- calculate_weighted_AP_dyadic(selected_d)
print(weighted_AP_dyadic)

```


```{r, plot weighted AP}


# Convert matrix to data frame
weighted_AP_df <- as.data.frame(weighted_AP_dyadic)

# Add row names as a column
weighted_AP_df$Respondent <- rownames(weighted_AP_df)

# Reshape data frame into long format
weighted_AP_long <- pivot_longer(weighted_AP_df, cols = -Respondent, names_to = "Party", values_to = "WAP")

# Generate heatmap
ggplot(data = weighted_AP_long, aes(x = Party, y = Respondent, fill = WAP)) +
  geom_tile(color = "white") +
  scale_fill_gradient(low = "lightblue", high = "darkblue") +
  labs(title = "Dyadic Weighted AP Scores", x = "Party", y = "Respondent") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1))


```



```{r}

add_non_zero_counts <- function(weighted_AP_dyadic) {
  # Count non-zero party preferences for each respondent
  non_zero_counts <- apply(weighted_AP_dyadic != 0, 1, sum)
  
  # Add non-zero counts as column 10
  weighted_AP_dyadic <- cbind(weighted_AP_dyadic, non_zero_counts)
  
  return(weighted_AP_dyadic)
}

weighted_AP_dyadic <- add_non_zero_counts(weighted_AP_dyadic)
print(weighted_AP_dyadic)

calculate_division <- function(weighted_AP_dyadic) {
  # Get the non-zero counts from column 10
  non_zero_counts <- weighted_AP_dyadic[, 10]
  
  # Divide values for each respondent's party preferences row-wise and store in new columns 11-19
  for (i in 1:nrow(weighted_AP_dyadic)) {
    # Get the values for the respondent
    respondent_values <- weighted_AP_dyadic[i, 1:9]
    
    # Calculate the division factors (non-zero counts for the respective respondent)
    division_factors <- non_zero_counts[i]
    
    # Initialize new column indices
    new_column_indices <- 11:19
    
    # Divide values by the division factor and store in new columns
    # Skip division if the party preference is zero
    for (j in 1:9) {
      if (respondent_values[j] != 0) {
        weighted_AP_dyadic[i, new_column_indices[j]] <- respondent_values[j] / division_factors
      } else {
        weighted_AP_dyadic[i, new_column_indices[j]] <- 0
      }
    }
  }
  
  return(weighted_AP_dyadic)
}




weighted_AP_dyadic <- calculate_division(weighted_AP_dyadic)
Sorryprint(weighted_AP_dyadic)

```













```{r, WAP dyadic (previous model)}
calculate_affective_polarization_party <- function(data, scaling_factor) {
  party_pref_vars <- c("IMD3008_A", "IMD3008_B", "IMD3008_C", "IMD3008_D", 
                       "IMD3008_E", "IMD3008_F", "IMD3008_G", "IMD3008_H", "IMD3008_I")
  
  vote_share_vars <- c("IMD5001_A", "IMD5001_B", "IMD5001_C", "IMD5001_D", 
                       "IMD5001_E", "IMD5001_F", "IMD5001_G", "IMD5001_H", "IMD5001_I")
  
  affective_polarization_scores <- matrix(0, nrow = nrow(data), ncol = length(party_pref_vars))
  
  for (i in 1:nrow(data)) {
    party_pref <- unlist(data[i, party_pref_vars])
    vote_share <- unlist(data[i, vote_share_vars]) 
    
    # Initialize affective polarization scores for the current respondent
    affective_polarization_row <- rep(0, length(party_pref))
    
    # Calculate the average like-dislike score for the current respondent
    valid_ratings <- which(!is.na(party_pref) & party_pref != 99)
    likei <- sum(party_pref[valid_ratings] * vote_share[valid_ratings])
    
    # Calculate the affective polarization score for non-missing party preferences
    valid_parties <- party_pref != 99
    affective_polarization_row[valid_parties] <- sqrt(vote_share[valid_parties] * (party_pref[valid_parties] - likei)^2)
    
    # Store the scaled affective polarization scores for the current respondent
    affective_polarization_scores[i, ] <- affective_polarization_row * scaling_factor
  }
  
  return(affective_polarization_scores)
}

# Example usage:
scaling_factor <- 0.1  # Adjust the scaling factor as needed
affective_polarization_party_scores <- calculate_affective_polarization_party(selected_d, scaling_factor)
print(affective_polarization_party_scores)

```








```{r, match matrix }
# a matrix data frame called matrix_with_parties where rows represent respondents and columns represent parties (A to I)
# a dyadic data frame called dyadic_data with columns 'from_party', 'to_party', and 'value'

# Add columns for 'from_party' and 'to_party' to the matrix
matrix_with_parties$from_party <- NA
matrix_with_parties$to_party <- NA

# Iterate over each row in the dyadic data
for (i in 1:nrow(dyadic_data)) {
    from_party <- dyadic_data$from_party[i]
    to_party <- dyadic_data$to_party[i]
    value <- dyadic_data$value[i]  # Assuming you have a value associated with each dyadic relationship
    
    # Find the corresponding row index in the matrix
    respondent_index <- match(dyadic_data$respondent[i], matrix_with_parties$respondent)
    
    # Update the 'from_party' and 'to_party' columns in the matrix
    matrix_with_parties$from_party[respondent_index] <- from_party
    matrix_with_parties$to_party[respondent_index] <- to_party
    
    # Optionally, you can also update the value associated with the dyadic relationship in the matrix
    # matrix_with_parties[respondent_index, paste0("value_", from_party, "_to_", to_party)] <- value
}

# Now matrix_with_parties should have 'from_party' and 'to_party' columns integrated

```









